### 2021-02-15 results.tex
second revision result,backgroud,setup. threats first version

Our first study performed a non-exact replication of Bao et al work.
Our study differs from the original because here we isolated the effect
of the DroidFax static analysis algorithms in the performance to
identify malicious apps using the test case generation tools for
mining sandboxes. In addition, we discarded six pairs of
Android apps we were not able to instrument---out of the $102$ pairs used in the \original work.
\rb{All of this following information should be detailed in
the study settings, and not repeated here if it is already there.} {\color{red}We also introduced a recent test generator tool, that has not been considered at previous work, Humanoid, and different from the original study, we expand the execution time of each test generation tool, executing each app at each tool for three minutes, while the original study executed for just one minute. The purpose of this time expansion is to check if the test generation tool code coverage results are consistent with Bao et al. results.}

As discussed in the previous section, we first executed the analysis using the DroidXP benchmark with its default configuration. After that, we executed the analysis again though disabling the DroidFax static analysis algorithm, so that we could better estimate the performance of the dynamic analysis tools for mining Android sandboxes. Table~\ref{tab:fs} summarizes the results of the execution. The columns Exec. (I) and Exec. (II) 
show the number of malwares identified when executing each tool (I) with the
support of the DroidFax static analysis algorithms and (II) without the support
of DroidFax static analysis algorithms. The Improvement column shows the impact
(in percentage) of DroidFax static analysis algorithms in the results.
In the previous work~\cite{}, the authors do not present a
discussion about the influence of DroidFax in the results, even
though here we report that this difference is in the
range from 23.94\% (Monkey) to 69.39\% (Humanoid)---discarding our
\joke tool for which DroidFax improves its performance in 100\% (as expected).
Next we discuss the result of each individual test generation tool.

>>>>

Our first study performed a non-exact replication of Bao et al work.
%\kn{We should introduce an abbreviation for the Bao et al work and reuse it everywhere. What do you think? }. 
As discussed in the previous section, we first executed the analysis using the DroidXP benchmark with its default configuration. After that, we executed the analysis again though disabling the DroidFax static analysis algorithm, so that we could better estimate the performance of the dynamic analysis tools for mining Android sandboxes. Table~\ref{tab:fs} summarizes the results of the execution. The columns Exec. (I) and Exec. (II) 
show the number of malwares identified when executing each tool (I) with the
support of the DroidFax static analysis algorithms and (II) without the support
of DroidFax static analysis algorithms. The Improvement column shows the impact
(in percentage) of DroidFax static analysis algorithms in the results.
In the previous work~\cite{}, the authors do not present a
discussion about the influence of DroidFax in the results, even
though here we report that this difference is in the
range from 23.94\% (Monkey) to 69.39\% (Humanoid)---discarding our
\joke tool for which DroidFax improves its performance in 100\% (as expected).
Next we discuss the result of each individual test generation tool.

### 2021-02-15 setup.tex
second revision result,backgroud,setup. threats first version

We conducted two studies to answer the research questions above. First we performed a non-exact replication of Bao et al work.
For that purpose, we initially selected four test generation tools: Droidbot~\cite{DBLP:conf/icse/LiYGC17},
DroidMate~\cite{DBLP:conf/icse/JamrozikZ16}, Monkey~\cite{Monkey}, and Humanoid~\cite{DBLP:conf/kbse/LiY0C19}. The first three have
been explored in the original work of Bao et al.~\cite{DBLP:conf/icse/JamrozikZ16}. We selected Droidbot and DroiMate because they achieved
the best performance on detecting malicious behavior at $102$ pairs of Android apps (B/M) at Bao et al work. We also considered the open source tool from Google, Monkey, because it is the most widely used tool in industry \cite{DBLP:conf/sigsoft/ZengLZXDLYX16}, coming up with the Android SDK installation. Monkey was developed for stress testing and can not perform text input. Therefore, we also selected Humanoid, that emulate realistic users, creating human-like test inputs using deep learning techniques.
For this non-exact replication, we also used the DroidXP benchmark~\cite{DBLP:conf/scam/CostaMCMVBC20},
which helped us to reproduce the original work.

@@

We investigate the four test case generation tools described earlier and added a fake test
case generation tool (named Joke) that simulates a test tool that does not execute
the Android apps during a benchmark execution. Using this tool, the results
of the dynamic analysis are not considered and we can compute the results with
only the static analysis component of DroidFax (RQ1). Our study executed each pairs of
Android app (B/M) in each one of the five test generation tools, including Joke,
for three minutes. We then investigate the performance of each tool to detect
malicious behaviors in the sandbox modeled by the test generation tool
under analysis.

>>>>

We conducted two studies to answer the research questions above. First we performed a non-exact replication of Bao et al work. Our study differs from the original because here we isolated the effect of the DroidFax static analysis algorithms in the performance to identify malicious apps using the test case generation tools for
mining sandboxes. In addition, we discarded six pairs of
Android apps we were not able to instrument---out of the $102$ pairs used in the original work. We also introduced a recent test generator tool, that has not been considered at previous work, Humanoid ~\cite{DBLP:conf/kbse/LiY0C19}, and different from the original study, we expand the execution time of each test generation tool, executing each app at each tool for three minutes, while the original study executed for just one minute.

The other $3$ test generation tools selected were: Droidbot~\cite{DBLP:conf/icse/LiYGC17},
DroidMate~\cite{DBLP:conf/icse/JamrozikZ16} and Monkey~\cite{Monkey}, all explored at the original work of Bao et al.~\cite{DBLP:conf/icse/JamrozikZ16}. We selected Droidbot and DroiMate because they achieved
the best performance on detecting malicious behavior at $102$ pairs of Android apps (B/M) at Bao et al work. We also considered the open source tool from Google, Monkey, because it is the most widely used tool in industry \cite{DBLP:conf/sigsoft/ZengLZXDLYX16}, coming up with the Android SDK installation. Since Monkey was developed for stress testing, and can not perform text input, we also considered Humanoid, that emulate realistic users, creating human-like test inputs using deep learning techniques.
For this non-exact replication, we also used the DroidXP benchmark~\cite{DBLP:conf/scam/CostaMCMVBC20},
which helped us to reproduce the original work.

@@

We investigate the four test case generation tools described earlier and added a fake test
case generation tool (named Joker) that simulates a test tool that does not execute
the Android apps during a benchmark execution. Using this tool, the results
of the dynamic analysis are not considered and we can compute the results with
only the static analysis component of DroidFax (RQ1). Our study executed each pairs of
Android app (B/M) in each one of the five test generation tools, including Joker,
for $3$ minutes. We then investigate the performance of each tool to detect
malicious behaviors in the sandbox modeled by the test generation tool
under analysis.
